Model Adaptivity for Goal-Oriented Inference

### 2015-05-20 practice/docs/thesis/cover_ack_abstract.tex
final thesis draft

\title{\large should probably decide whether to include chad's thing...}
%\fontsize{15}{17}\selectfont 
\author{Harriet Li}

@@

...

>>>>

\title{Model Adaptivity for Goal-Oriented Inference}
%\fontsize{15}{17}\selectfont 
\author{Harriet Li}

@@

This work would not have been possible without the help of many others, whom I hope I have, or will be able to, thank in more meaningful ways than I am able to here.

I am most deeply grateful to my advisor, Professor Karen Willcox, for her support and guidance throughout my undergraduate years and in my graduate studies, for allowing me to explore the realm of research and computational methods through UROPs when I was curious but clueless, for suggesting new directions whenever I ran myself into a corner, and for helping me work around what I feared were fatal weak points in my self.

I am also very grateful to Dr. Vikram Garg, for allowing me to run with his ideas, for being patient in explaining new concepts, for describing these concepts in ways that were accessible to me even though my background was lacking, and for being the opposite of the scary person I was expecting when he was first introduced to me.

I thank my parents, for doing their best to give me the freedom to pursue my interests, for being supportive of my choice to stay in school and conduct research even though I could no longer explain my work to them, and for forgiving me when I forgot their birthdays or to return their calls during the busiest times of the year. I thank my sister, for listening and reminding me of life outside of research.

I thank my friends, for keeping me sane, for tempting me to take breaks and keeping me company when I refused, for providing baked goods when I began to regret my dislike for coffee, for listening when I was upset and allowing me to reciprocate, for being interesting people with interesting stories and interesting personalities.

And I thank Dr. Bart van Bloemen Waanders, for allowing me to work with him over summers and explore areas of computational science outside of my thesis work.

This work was supported by the United States Department of Energy, Office of Advanced Scientific Computing Research (ASCR), Applied Mathematics Program, awards DE-FG02-08ER2585 and DE-SC0009297, as part of the DiaMonD Multifaceted Mathematics Integrated Capability Center.
